---
title: "My CV"
name: "Jia Yee"
surname: "Wong"
position: "Student at University of Nebraska-Lincoln"
pronouns: "She/Her"
email: '<a href="mailto:jiayeewongjy05@gmail.com">jiayeewongjy05@gmail.com</a>'
github: '<a href="https://github.com/jiayeew">jiayeew</a>'
linkedin: '<a href="https://www.linkedin.com/in/jiayee-wong/">jiayee-wong</a>'
date: "`r format(Sys.time(), '%B %Y')`"
output:
  vitae::awesomecv:
    page_total: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Summary
Data Scientist undergraduate student with <1 years of experience focusing on **Statistical Modeling, Artificial Intelligence, and Data Pipeline**.

# Skills
**Programming:** Python, SQL, R, HTML, JAVA\
**Software:** Microsoft Office, Tableau, SAS, MATLAB\
**Language:** English, Chinese, Cantonese, Malay, Korean


#  Education

```{r}
library(tibble)
tribble(
  ~Role, ~Company, ~Where, ~Dates, ~Details,
  
  # UNL
 "Major in Data Science, Minor in Statisitcs and Data Analytics", "Lincoln, Nebraska", "University of Nebraska-Lincoln",  "Aug 2023 - May 2026", "Dean's List: Fall 2023, Spring 2024",
 "Major in Data Science, Minor in Statisitcs and Data Analytics", "Lincoln, Nebraska", "University of Nebraska-Lincoln",  "Aug 2023 - May 2026", "Relavant Coursework: Data Structure and Algorithm, Data Analysis, Database System, Deep Learning, Machine Learning and Linear Regression."

) %>%
detailed_entries(Role, Company, Where, Dates, Details)
```


#  Work Experience

```{r}
tribble(
  ~Role, ~Company, ~Where, ~Dates, ~Details,
  
  # GE
 "Data Scientist Intern", "Kuala Lumpur, Malaysia", "Great Eastern Life Assurance (Malaysia)",  "May 2024 - Aug 2024", "Employed NumPy and pandas in Python for data cleaning, manipulation, and analysis, streamlining workflows and enhancing data-driven decision-making.",
 "Data Scientist Intern", "Kuala Lumpur, Malaysia", "Great Eastern Life Assurance (Malaysia)", "May 2024 - Aug 2024", " Performed data verification, validation, and analysis using Excel, significantly increasing validation efficiency, and ensuring accuracy to provide actionable insights.",
 "Data Scientist Intern", "Kuala Lumpur, Malaysia", "Great Eastern Life Assurance (Malaysia)", "May 2024 - Aug 2024", "Proactively identified and rectified missing, duplicate, and outlier data points, reducing errors by 20% and enhancing overall data integrity.",
 "Data Scientist Intern", "Kuala Lumpur, Malaysia", "Great Eastern Life Assurance (Malaysia)",  "May 2024 - Aug 2024", "Leveraged Tableau to develop interactive reports and dashboards, enabling agile decision-making.",
 
 # Starbucks
 "Barista", "Lincoln, Nebraska", "Starbucks, Nebraska Union ", " Oct 2023 - Present", "Handcrafted drinks for on-campus students in a fast-paced environment.", 
 "Barista", "Lincoln, Nebraska", "Starbucks, Nebraska Union ",  " Oct 2023 - Present", "Effectively worked with team members to ensure all orders were made accordingly and efficiently.", 
  "Barista", "Lincoln, Nebraska", "Starbucks, Nebraska Union ", " Oct 2023 - Present", "Ensured a clean and organized working environment by practicing food safety.", 
 
 # Tutor
 "Student tutor – CSCE 320: Data Analysis", "Lincoln, Nebraska","Husker Athletics", "Sep 2024 - Dec 2024","Delivered personalized tutoring sessions to student-athletes, simplifying complex SQL queries, Python programming, and data manipulation using Pandas for better comprehension and practical application.", 
 "Student tutor – CSCE 320: Data Analysis", "Lincoln, Nebraska", "Husker Athletics","Sep 2024 - Dec 2024","Guided student-athletes through hands-on projects involving data extraction, transformation, and analysis with SQL and Python, ensuring a strong grasp of key concepts in data analysis.", 
 
 
) %>%
detailed_entries(Role, Company, Where, Dates, Details)
```



# Projects

## Light Rail Transit Database Model | Sep 2024 - Dec 2024
- Developed and implemented a relational database model for a light rail transit system, connecting Omaha and Lincoln, Nebraska
- Designed and implemented an optimized SQL schema and developed dynamic queries for practical applications
- Collected, transformed, and visualized geospatial data using MATLAB, applying piecewise linear approximations to model train routes, compute distances, and present routes on a geographic map

## Deep Reinforcement Learning Agent for Pac-Man | Aug 2024 - Dec 2024
- Developed a Deep-Q-Network (DQN) agent to play Pac-Man, using decision-making to maximize cumulative rewards and gameplay effectiveness
- Implemented a convolutional neural network (CNN) to process grayscale images, allowing spatial feature recognition for action selection
- Configured the Atari environment for game-state tracking and integrated frame-skip techniques to improve computational efficiency
- Monitored model performance using metrics such as average score and win rate to achieve improved gameplay and strategic responsiveness.